---
title: "index"
output: html_document
---

##Indroduction
Here you will take your chance to explore some of the significant changes throughout our planet earth. Through centuries we discuss the topic of global crisis, such as increasing of temperature, weather changes, and they are primarly cause by level carbon dioxide changes. 
Anyone interested in how Earth is changing could use this data, and it could improve their fundamental understanding. Questions we will be focusing are “How are the Carbon dioxide level changing?” and “Where does Carbon dioxide is coming from, and is it increasing/decreasing?” We will help these general audience’s question, and we believe the data we will provide will help them understand better. 

To help focus on learning about the change of carbon dioxide throughout the globe. Thanks to ESRL, the Earth System Research Laboratory, we will have very simple access to the recorded data set since the year 1958 to the year 2018. And from CDIAC, the Carbon Dioxide Information Analysis Center, we gather the data that filed with different sources that creates Carbon dioxide and how much they have changed as the time goes by since the 1700s.


```{r setup, include=FALSE}
library(shiny)
library(ggplot2)
library(dplyr)
library(R.utils)
knitr::opts_chunk$set(echo=FALSE, message=FALSE)
source("climate_stats/server.R")
source("climate_stats/ui.R")
```

## Data 1

Let’s take a look at the Average Carbon dioxide level world wide, here we could understand better of just how much have change throughout the world by average. Here we have the graph that display the change of Carbon dioxide level in our Atmosphere from 1958 to 2019.

```{r cars}
summary(cars)
```

We can observe the simple pattern since the beginning, the patterns are not completely the same in every years but we can see there are always fall and rise, but by average it is constantly increasing every year.


## Data 2

Now let’s look at what is causing the CO2 level to rise every year and how much are they creating the Carbon Dioxide. This data set was recorded since 1751 but many of the source such as gas and liquid fuels were not in use until 1870.  The carbon emission is the term we use here and there are quite few. Main sources are from ofcourse, by fuel consumption, manufacturing and fire.

```{r pressure, echo=FALSE}
plot(pressure)
```

By looking at the data, we can observe that the CO2 level from all different source are constantly rising instead of dropping, we are constantly increasing the usage of fuels and manufacturing rate. Interesting changes we can observe is that the solid fuels were the dominant source of releasing Carbon Dioxide until 1968, since then liquid took the lead from any other source until the year of 1985. Which shows that since 1968 the liquid fuel has become more flexible and reliable but after the year 1985 the liquid fuel has decreased it's popularity.

## Conclusion
We have now have become very familiar that the level of CO2 is increasing as we observe the both plot.
So what does this all mean? and what does increasing level of CO2 means to us?
Unlike water vapor, Carbon dioxide remains a gas in almost any atmospheric temperature. When carbon dioxide level in the air decreases, Earth starts to cool, and some water vapor begins to separate off the atmosphere. But when carbon dioxide concentrations increases, air temperatures increases as well, and more and more water vapor evaporates into the atmosphere rather than fall, which then magnifies greenhouse heating.
Hence, Carbon dioxide is the gas that sets the temperature. Carbon dioxide controls the amount of water vapor in the atmosphere and thus the size of the greenhouse effect.
As is shown above the CO2 level is just steadily rising, which means it is changing the Earth temperature as we speak, and this matter requires extreme care. And we must be aware of this issue before it rises too high.